Residence time, a master variable of ecology, physiology, and natural selection

### 2015-09-15 analyses/ForPaper/PrimaryPredictions.Rmd
added new directory and files for a Hydrobide GUI -KL

```{r, results = 'hide', echo=FALSE, message = FALSE, warning = FALSE}
#install.packages("vegan") 
require("vegan") 
#install.packages("moments")
require("moments")
library(ggplot2)
```

@@

```{r, results = 'hide', echo=FALSE, message = FALSE, warning = FALSE}
## Load Data
 dat <- read.csv("~/GitHub/hydrobide/results/simulated_data/2015_September/7_Sept/SimData.csv")  
dat$h.tau <- (dat$height * dat$width)/dat$flow.rate
dat$total.abundance[dat$total.abundance<=0] <- 1
dat$species.richness[dat$species.richness<=0] <- 1

dat$e.var[dat$e.var =="NaN"] <- 1
dat$simpson.e[dat$simpson.e =="NaN"] <- 1

@@

```{r, results = 'hide', echo=FALSE, message = FALSE, warning = FALSE}
#install.packages("ISLR")
require(ISLR)

fit <- lm(log10(f.dat$total.abundance) ~ poly(log10(f.dat$h.tau), 2, raw=TRUE))
f.N.2.r2 <- summary(fit)$adj.r.squared
f.N.2.pVal <- anova(fit)$'Pr(>F)'[1]

>>>>

```{r, results = 'hide', echo=FALSE, message = FALSE, warning = FALSE}
#install.packages("vegan") 
require("vegan") 
#install.packages("moments")
require("moments")
#install.packages("IDPmisc", repos = "http://cran.cnr.Berkeley.edu")
require(IDPmisc)
#install.packages("ISLR")
require(ISLR)

library(ggplot2)
```

@@

```{r, results = 'hide', echo=FALSE, message = FALSE, warning = FALSE}
## Load Data
 dat <- read.csv("~/GitHub/hydrobide/results/simulated_data/2015_September/12_Sept/SimData.csv")
dat <- NaRV.omit(dat)
dat$h.tau <- (dat$height * dat$width)/dat$flow.rate

@@

```{r, results = 'hide', echo=FALSE, message = FALSE, warning = FALSE}
fit <- lm(log10(f.dat$total.abundance) ~ poly(log10(f.dat$h.tau), 2, raw=TRUE))
f.N.2.r2 <- summary(fit)$adj.r.squared
f.N.2.pVal <- anova(fit)$'Pr(>F)'[1]
